DOpElib:\\ Differential Equations and Optimization Environment

### 2017-04-12 Examples/Documentation/introduction.tex
Description modified w.r.t. to make c-all

>>>>

\subsection*{3.) Problem using make c-all in the Examples folder :}

\begin{lstlisting}
wick@linux:~/Software/dopelib/Examples> make c-all
cd OPT/StatPDE/Example1; make -s c-all
make[2]: *** No targets specified and no makefile found.  Stop.
../../../..//Examples/Make.global_options:2: recipe for target 'c-all' failed
make[1]: *** [c-all] Error 2
Makefile:24: recipe for target 'OPT/StatPDE/Example1' failed
make: *** [OPT/StatPDE/Example1] Error 2
\end{lstlisting}

This means that the Makefile in the specific examples folder has been 
modified in some illegal way. Remove this Makefile and get the original 
one from DOpElib. Then try again make c-all (make always sure that before 
typing make c-all that the deal.II path is exported - see above).
